Automated topic naming to support cross-project analysis of software maintenance activities

### 2011-01-26 msr/msr2011.tex
more abram editting

\section{Understanding software maintenance activities} 
\label{sec:analysis}
% \todo[inline]{talk about this topic in one section}
% \todo[inline]{reference project name Nomen more}
%In order to test  our ROC values produced acceptable results, we now turn to
%\emph{applying} those techniques to understand software maintenance
%activities. 
\todo[inline]{more on intro ... why should the reader care about this. It needs to show how the stuff in the intro (applications) is possible}
\todo[inline]{fix section headings}

We evaluated two research questions using the ground truth data that we
annotated by hand:
\begin{enumerate}
\item Do label frequencies change over time? Is a certain quality of more interest at one point in the life-cycle than some other? 
\item  Do the different projects differ in their relative topic interest? Is a particular quality more important to one project than the other projects?  
\end{enumerate}

@@

%\noindent \textbf{Understanding the figures} -- 
In Figure \ref{fig:mysql-timeline}, we see that the NFRs \emph{functionality}, \emph{portability} and \emph{maintainability} contain more labeled topics, since these NFRs have been more intensely shaded. % boxes. not sure boxes is important..
% I grepped query1.mrs2 http://softwareprocess.es/y/y/maxdb-76.tar.gz
% and                   http://softwareprocess.es/y/maxdb-7500.tar.gz
There are more \textsf{None} labels in MaxDB because a number of topics were to do with code cleanup or automated checking using tools like \texttt{sutcheck}, a tool-specific to the development process at MaxDB.

@@

Yes. MySQL 3.23 had proportionally more
topics labelled \emph{functionality}, while MaxDB had proportionally more
\emph{efficiency} related topics. MaxDB was a very mature release ``donated'' to the open-source community. 
MySQL, on the other hand, was in its relative infancy. 
Security problems were more common (security is a component of `functionality' in the ISO 9126 model). 
In both cases \emph{portability} was a constant maintenance concern and was prevalent throughout the entire lifetime of the projects.

\todo[inline]{link the actual data, which is interesting, to somethign actionable for a developer or manager}
\section{Discussion}
\label{sec:limit}

@@

\emph{Internal validity} -- %includes inter-rater reliability and our lack of rival explanation building. 
We improved internal validity by trying to correlate and explain the behaviours observed in the analysis with the historical records of the projects.
We did not attempt to match our results to any particular model or theory, as such theories are sparse in

>>>>

\section{Understanding software maintenance activities} 
\label{sec:analysis}
% \todo[inline]{talk about this topic in one section}
% \todo[inline]{reference project name Nomen more}
%In order to test  our ROC values produced acceptable results, we now turn to
%\emph{applying} those techniques to understand software maintenance
%activities. 
\todo[inline]{more on intro ... why should the reader care about
  this. It needs to show how the stuff in the intro (applications) is
  possible}
%%% XXX NEIL I don't get this.. VVVVV
%\todo[inline]{fix section headings}

In this section we investigate the history of the two projects that we
studied.
We demonstrate the value of topic analysis as it is capable of showing
the topic of development efforts over time in each project.
We evaluated two research questions using the ground truth data that we
annotated by hand:
\begin{enumerate}
\item Do label frequencies change over time? Is a certain quality of more interest at one point in the life-cycle than some other? 
\item  Do the different projects differ in their relative topic interest? Is a particular quality more important to one project than the other projects?  
\end{enumerate}

@@

%\noindent \textbf{Understanding the figures} -- 
In Figure \ref{fig:mysql-timeline}, we see that the NFRs \emph{functionality}, \emph{portability} and \emph{maintainability} contain more labeled topics, since these NFRs have been more intensely shaded. % boxes. not sure boxes is important..
% I grepped query1.mrs2 http://softwareprocess.es/y/y/maxdb-76.tar.gz
% and                   http://softwareprocess.es/y/maxdb-7500.tar.gz
There are more \textsf{None} labels in MaxDB because a number of topics were to do with code cleanup or automated checking using tools like \texttt{sutcheck}, a tool-specific to the development process of MaxDB.

@@

Yes. MySQL 3.23 had proportionally more
topics labelled \emph{functionality}, while MaxDB had proportionally more
\emph{efficiency} related topics. MaxDB was a very mature release ``donated'' to the open-source community. 
MySQL, on the other hand, was in its relative infancy. 
Security problems were more common (security is a component of \emph{functionality} in the ISO 9126 model). 
In both cases \emph{portability} was a constant maintenance concern and was prevalent throughout the entire lifetime of the projects.

\subsection{Summary}

\todo[inline]{link the actual data, which is interesting, to somethign
  actionable for a developer or manager}

\section{Discussion}
\label{sec:limit}

@@

\emph{Internal validity} -- %includes inter-rater reliability and our lack of rival explanation building. 
We improved internal validity by trying to correlate and explain the behaviours observed in the analysis with the historical records of the projects.
We did not attempt to match our results to any particular model or theory.
